\huge A Usability Evaluation of Tor Launcher

### 2017-02-28 pets2017-paper/pets2017-paper.tex
change word

To help users decide what to do, we label the configure button as an option heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation.

>>>>

To guide users, we label the configure button as an option heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation.
